A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-08 paper.tex
Fix typos and missing labels

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item We investigate the usage of DLTs and distribute data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
\end{itemize}

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of data exchange mechanisms for IoT, decentralized data trading infrastructures and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion}.

@@

@@

\begin{table*}[h]
	\caption{Data Price Estimation}
	\label{tab:ether}
	\centering
	\resizebox{0.8\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
		\hline
		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
		\hline
		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
		\hline
		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
		\hline
		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
		\hline
	\end{tabular}
	}
\end{table*}
\subsection{MAM vs. the delegated MAM}
What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes. Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too. The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.

@@

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

>>>>

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
\end{itemize}

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the componets of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion}.

@@

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}
What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes. Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too. The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.

@@

\begin{table*}[h]
	\caption{Data Price Estimation}
	\label{tab:ether}
	\centering
	\resizebox{0.8\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
		\hline
		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
		\hline
		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
		\hline
		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
		\hline
		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
		\hline
	\end{tabular}
	}
\end{table*}

@@

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
